---
title: "simulation"
author:  "Alexey Abramov"
date: "11/9/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(rvest)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

Examples 

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 4) {
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)
    )

  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}
```

I can "simulate" this

```{r}
sim_mean_sd(30)
```

But now let's really do it with a  for loop.

```{r}
output = vector("list", length = 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(samp_size = 30)
}

bind_rows(output)
```

Lets use a loop function.

```{r}
sim_results =
  rerun(100, sim_mean_sd(samp_size =30)) %>% 
  bind_rows()


```

Let's try other sample sizes
n = 30 is the name of the elements in the list.

```{r}
n_list = 
  list(
    "n = 30" = 30,
    "n = 60" = 60,
    "n = 120" = 120,
    "n = 500" = 500)

output = vector("list", length = 4)

output[[1]] = rerun(100, sim_mean_sd(samp_size = n_list[[1]])) %>% 
  bind_rows()
```
 
 
Now a for loop!

```{r}
for (i in 1:4) {
  
  output[[i]] = rerun(100, sim_mean_sd(samp_size = n_list[[i]])) %>% 
  bind_rows()
  
}
```

.x is the argument that goes INSIDE of rerun function
Rerun here is spitting out lists and now into a dataframe
And now we want to UN-NEST it

```{r, cache = TRUE}
sim_results = 
  tibble(
  sample_size = c(30, 60, 120, 500)) %>% 
    mutate(
      output_lists = map(.x = sample_size, ~ rerun(100, sim_mean_sd(.x))),
      estimate_df = map(output_lists, bind_rows)
      ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)
```

Do some dataframe things

Rename the sample_size column 
And reorder them

```{r}
sim_results %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>% 
  ggplot(aes(x = sample_size, y = mean)) +
  geom_boxplot()
```

Summarize
```{r}
sim_results %>% 
  group_by(sample_size) %>% 
  summarize(
      avg_sample_mean = mean(mean),
      sd_sample_mean = sd(mean)
      )
```


